Deciding to Disclose: Pregnancy and Alcohol Misuse

### 2014-07-08 Methods.tex
Adding algorithms

\begin{table}
\center
\begin{tabular} {|l | c | r|}
\hline
Name & Description & Value \\ \hline
\(N_{w}\) & Number of women & 1000 \\ \hline
\(N_{m}\) & Number of midwives & 100 \\ \hline
k & Number of appointments per midwive & 1000 \\ \hline
A & Maximum number of appointments per woman & 12 \\ \hline
R & Runs & 1000 \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(p_{w}\) & Probability of women sharing & 0. \\ \hline
\(q_{w}\) & Weight of shared information for women & 0. \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 10 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
 \cite{Bijak2013b}

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

To better capture the response characteristics for the model, we employ three - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3) the standard deviation of that average signal between simulation runs. Together these three metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the stability of the system in the face of the stochastic elements.

@@

Twelve emulators were built, covering each of the three output on all four decision models. These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination. In addition, the trained emulators were used to explore novel areas of the parameter space.?????????????

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(p_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(q_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(Payoff_{baby}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(Payoff_{referral}\) & Cost for referral & \multicolumn{2}{l|}{\(Payoff_{baby} - 1\)} \\ \hline
\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 1 & 100 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

>>>>

\begin{table}
\center
\begin{tabular} {|l | c | r|}
\hline
Name & Description & Value \\ \hline
\(N_{w}\) & Number of women & 1000 \\ \hline
\(N_{m}\) & Number of midwives & 100 \\ \hline
\(A_{m}\) & Number of appointments per midwive & 1000 \\ \hline
\(A_{w}\) & Maximum number of appointments per woman & 12 \\ \hline
R & Runs & 1000 \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & \(1/3\) \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & \(1/3\) \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & \(1/3\) \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & \(5/100\) \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & \(10/100\) \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & \(85/100\) \\ \hline
\(p_{w}\) & Probability of women sharing & 0. \\ \hline
\(q_{w}\) & Weight of shared information for women & 0. \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0. \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0. \\ \hline
\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 10 \\ \hline
\end{tabular}
\caption[Table caption text]{Model parameters. \label{tab:qt_params}}
\end{table}
\subsection{Global Sensitivity Analysis}
\label{sub:sensitivity}
%Maxmin latin hypercube -> remember to cite the r package used.
%Will require some discussion of the gemsa technique at this point - can also cite Jason H for precedent!
 \cite{Bijak2013b}

Parameters for training were generated in R \citep{RTeam2014} using Latin Hypercube Sampling \citep{Carnell2012} over the space of inputs given in table \ref{tab:sa_params}, giving 10 free parameters. Initially a unit hypercube was generated, then the margins transformed appropriately to cover those regions where the inputs are not bounded between 0 and 1, and for proportions of agent types which necessarily sum to one across the three parameters. Given the limitation of 400 design points for the \ac{GEM-SA} software, we produced exactly that many parameter combinations and collected results for 100 runs of each. A fixed set of 100 random seeds was used, such that each parameter set was run once with each seed, for every decision rule.

To better capture the response characteristics for the model, we measure three outcome variables - (1) the interquartile range of the average signal sent by each type of agent in a run, (2) the average signal of moderate drinking agents in a run, and (3) the standard deviation of that average signal between simulation runs. Together these three metrics give an indication of how far women are separable by their signalling behaviour (1), the behaviour of the at risk drinking groups\footnote{Under most conditions, the behaviour of heavy drinkers tracks closely with their moderate counterparts.} (2), and finally the stability of the system in the face of the stochastic elements.

@@

Twelve emulators were built, covering each of the three output on all four decision models. These emulators were used to conduct a probabalistic sensitivity analysis using \ac{GEM-SA} to assess the impact of parameters individually, and in combination.

\begin{table}
\center
\begin{tabular} {|l | l | l| l|}
\hline
Name & Description & Min & Max \\ \hline
\(P_{h,w}\) & Proportion of heavy drinkers & 0 & 1 \\ \hline
\(P_{m,w}\) & Proportion of moderate drinkers & 0 & 1 \\ \hline
\(P_{l,w}\) & Proportion of light drinkers & 0 & 1 \\ \hline
\(P_{h,m}\) & Proportion of harsh midwives & 0 & 1 \\ \hline
\(P_{m,m}\) & Proportion of moderate midwives & 0 & 1 \\ \hline
\(P_{l,m}\) & Proportion of non-judgemental midwives & 0 & 1 \\ \hline
\(p_{w}\) & Probability of women sharing & 0 & 1 \\ \hline
\(q_{w}\) & Weight of shared information for women & 0 & 1 \\ \hline
\(p_{m}\) & Probability of midwives sharing & 0 & 1 \\ \hline
\(q_{m}\) & Weight of shared information for midwives & 0 & 1 \\ \hline
\(Payoff_{baby}\) & Health payoff for healthy delivery & 1 & 100 \\ \hline
\(Payoff_{referral}\) & Cost for referral & \multicolumn{2}{l|}{\(-(Payoff_{baby} - 1)\)} \\ \hline
\(s_{i}[a_{i}]\) & Psuedo-count favouring honesty & 1 & 100 \\ \hline
\end{tabular}
\caption[Table caption text]{Parameter ranges. \label{tab:sa_params}}
\end{table}

### 2014-07-08 Model.tex
Adding algorithms

Midwives play for \(k\) rounds (\(k=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

\begin{table}
\center
\subfloat[Social cost\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Health outcome\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Referral cost\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9, 0 & -9, 0 & -9, 0\tabularnewline
\cline{2-5} 
 & Don't refer & 0, 0 & 0, 0 & 0, 0\tabularnewline
\hline 
\end{tabular}

@@

A simplifying assumption is made that all midwives have just qualified, with identical training and as a result have entirely homogenous beliefs about their women. It is assumed in general that they have not been trained by Dr. House, and as a result have been taught that people will generally tell the truth.
Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible at least once, with exactly \(k\) encounters overall.

\subsubsection{Payoff Reasoning}

Both payoff reasoners assume a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between lotteries. The lexicographic heuristic (algorithm \ref{alg:lexicographic}) maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. The Bayesian risk minimisation agent uses the same subset of information, but updates beliefs on the link between actions and payoffs using Bayes rule, and attempts to choose the action which minimises risk.

@@

Aside from the heuristic agent, the remaining three agent types use Bayesian updating to attempt to improve
the accuracy of their beliefs. Given the discrete nature of agent
types, and actions, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed to represent these beliefs. The probability
density function takes the form -

Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of discrete types, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the integer
psuedo-count of prior observations for type \(i\).

The distribution is particularly convenient, in that to infer the
probability of a new observation being of some particular type becomes
simply -

Where \(n_{j}\) is simply the count of occurrences of type \(j\), so
that the belief that a new observation is of type \(j\) the number
of times that type has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.

@@

The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans. While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{Hau2008}. In this instance we replace the frequentist first stage with the equivalent Bayesian inference process.

@@

By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent discount implausible outcomes.

>>>>

Midwives play for \(A_{m}\) rounds (\(A_{m}=1000\) in all experiments), and conduct appointments in parallel, i.e. if there are 5 midwives, then five women are drawn from the queue and assigned at random to the midwives. 
Unlike women, midwives are only informed of their payoff if they choose to make a referral. Both groups of agents have perfect recall, and midwives are assumed to retrospectively update their observations if they make a referral after a number of appointments.

\begin{table}
\center
\subfloat[Social cost, \(P_{s}\)\label{tab:Social-cost-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Health outcome, \(P_{h}\)\label{tab:Referral-payoff-matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5} 
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline

@@

\subfloat[Referral cost, \(P_{c}\)\label{tab:inst_cost_matrix}]{%
\begin{tabular}{|c|c|c|c|c|}
\cline{3-5}  
\multicolumn{2}{c}{} & \multicolumn{3}{|c|}{Woman}\tabularnewline
\hline 
\multirow{3}{*}{\rotatebox[origin=c]{90}{Midwife}} &  & Heavy & Moderate & Light\tabularnewline
\cline{2-5} 
 & Refer & -9, 0 & -9, 0 & -9, 0\tabularnewline
\cline{2-5} 
 & Don't refer & 0, 0 & 0, 0 & 0, 0\tabularnewline
\hline 
\end{tabular}

@@

A simplifying assumption is made that all midwives have just qualified after receiving identical training. As a result, they have homogenous beliefs about their women and assume to some extent that they are honest.
Women are heterogenous in their prior observations, which are assigned stochastically and constrained such that they have encountered each scenario possible at least once, with exactly \(k\) encounters overall.

Formally we let \(S\) be the set of signals \(\{l, m, h\}\), \(T_{w}\) be the set of drinking types \(\{l, m, h\}\), \(T_{m}\) the set of midwife types \(\{l, m, h\}\), and \(J=\{r,n\}\) the actions available to midwives. The set of all payoffs shall be denoted \(P\), where \(P_{w}\) are the payoffs for all women\footnote{While it is assumed that \(P_{w}\) for an individual of type \(a\) is constrained such that \(T=\{a\}\), this can change under the modified game described in subsection \ref{sub:info_sharing}} defined by \(P_{w}=\{x | x=P_{h, b, c} + P_{s, a, d}\wedge b \in J\wedge c \in T\wedge d \in M\}\), and equivalently for midwives \(P_{m}=\{x | x=P_{h, b, c} + P_{c, b}\}\).

\subsection{Lexicographic Heuristic}
\label{sub:lexico}

The lexicographic heuristic (algorithm \ref{alg:lexico}) follows the form of that used in \cite{Hau2008}, and assumes a simplified decision problem, as in figure \ref{fig:payoff_problem}, where an action is a choice between combined lotteries. Functionally, the heuristic maintains a count of the number of times that each action was followed by a payoff, and chooses the action which most commonly has the best payoff, i.e. one reason decision making. This approach requires minimal computation, and does not assume that all payoffs are known, or static.

Women maintain a count, \(n\) for each of the \(k\) payoffs in \(P_{w, a},a\in k\), an individual payoff paired with a signal, such that \(n_{i}=\{n_{i,1}\ldots n_{i,k}\}\).

Midwives solve a slightly different problem, where the signal received may convey useful information. This is resolved by maintaining a separate count for each signal, i.e. \(n_{i,j}=\{n_{i,j,1}\ldots n_{i, j, k}\}\), and otherwise follow the same algorithm.

\begin{algorithm}
\begin{algorithmic}
\State n=1, action=none
\While{action is none}
\State Calculate the nth most common outcome following each action.
\State Sort actions by the value of the nth most common outcome.
\If{clear winner} \State action = best \EndIf
\State n = n + 1
\EndWhile
\State \Return action
\end{algorithmic}
\caption{Lexicographic heuristic\label{alg:lexico}}
\end{algorithm}

\subsubsection{Bayesian Payoff Heuristic}

The Bayesian payoff agent uses the same subset of information as the lexicographic method, but updates beliefs on the link between actions and payoffs using Bayes rule, and attempts to choose the action which minimises risk.

Given the discrete nature of actions and payoffs, coupled with a desire for tractability of the
simulation, the Dirichlet distribution is employed to represent these beliefs. The probability
density function takes the form -

Where \(\alpha=\{\alpha_{1}\ldots\alpha_{k}\}\), \(k\) is the number
of signal-payoff pairs, \(\Theta=\{x_{1},\,\ldots,x_{k-\text{1}}\}\) all
more than zero and summing to less than 1, and \(\alpha_{i}\) is the integer
psuedo-count of prior observations for a pair \(i\).

The distribution is particularly convenient, in that to infer the
probability of a signal implying a payoff becomes
simply -

Where \(n_{j}\) is simply the count of occurrences of pair \(j\), so
that the belief that a signal \(j\) the number
of times that type has been observed (including the pseudo-count),
over the total number of observations thus far. This makes computation
of beliefs fast and simple, since all that must be maintained is
a count of observations with no particular concern as to their order.

As before, midwives follow a similar pattern but per signal.

@@

The second Bayesian agent augments the payoff reasoning version by separating the two lotteries and assuming that \(P\) is a static, and known set of payoffs possible for the agent. For women, this means that they maintain two sets of beliefs: a Dirichlet mixture which represents the believed distribution of midwife types, and a second set linking signals to referrals.

Formally, let \(D=\{D_{h}, D_{s}\}\), \(\alpha=\{\alpha_{h},\alpha_{s}\}\), and \(n=\{n_{h},n_{s}\}\). The quantity to be minimised then becomes -

\begin{equation}
R(i)= \sum_{z=1}\sum_{j=1}-P_{w, i, z, j}P(x=l|D_{s},\alpha_{s})P(x=j|D_{h},\alpha_{h})\label{eq:risk}
\end{equation}

So that the risk of a signal, \(i\) is the sum of all possible payoffs multiplied by the probability of that payoff occurring.

Midwives reasoning centers determing the meaning of signals, since given the knowledge of what some signal \(i\) conveys about the true type of the sender, the payoff for an action is known. As such, their inference process is the same as for the simple Bayesian agent but over signal-type pairs, and they attempt to minimise -

\begin{equation}
R(i, j)= \sum_{z=1}\sum_{j=1}-P_{m, i, z, j}P(x=l|D_{s},\alpha_{s})P(x=j|D_{h},\alpha_{h})\label{eq:mw_risk}
\end{equation}

@@

The most complex decision rule used is \ac{CPT}, which attempts to reproduce a number of systematic deviations from rationality observed in humans. While \ac{CPT} has primarily been applied in the context of decisions from description, it has been modified to deal with decisions from experience by incorporating a first stage where probabilities are estimates from observations as in \cite{FoxCPT}. In this instance we replace the frequentist first stage with the equivalent Bayesian inference process.

@@

By contrast, representing the problem in terms of the probabilities of the individual lotteries yields a structure that abstracts the new information from payoffs, and allows the agent discount implausible outcomes. This stronger assumption as to the static and known qualities of payoffs does however reduce the flexibility of the decision rule.
